---
title: "Birdie Webscrape"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)

```
Get Birdie Webpage
```{r}
## Get webpage
webpage <- read_html("https://www.eventhubs.com/tiers/sf5/character/birdie/")

##Get tables of interest
tbls <- html_nodes(webpage, "table") 

table_out <- tbls %>% html_table()

filter_table <- table_out[1:3]
## Bind tables of interest
birdie_table <- do.call(rbind, filter_table)


birdie_table
```

## Notes/idea
- Maybe weight on the amount of votes each matchup gets
We can use each games page to scrape for chracter names

Prepare birdie table for being a part of the 
```{r}
birdie_table %>% select(Character, `Match avg.`) %>%
  column_to_rownames(var = "Character") %>%
  rename(Birdie = `Match avg.`)
```
Scrape the names of all the games
```{r}
tier_games_url <- read_html("https://www.eventhubs.com/tiers/")
tbls <- html_nodes(tier_games_url, "table") 

table_out <- tbls %>% html_table()
game_titles <- table_out[[3]][,2]
```
## GOtta pull the specific links from the table I selected
```{r}
tier_games_url <- read_html("https://www.eventhubs.com/tiers/")



tbls <- html_nodes(tier_games_url, "table") 

all_games <- tbls[3] %>%
      html_nodes("td a") %>%
      html_attr('href')

table_out <- tbls %>% html_table()
game_titles <- table_out[[3]][,2]

game_links <- paste0("https://www.eventhubs.com", all_games)
## Remove extra /
game_links <- unique(gsub("[/]$", "",game_links))
```

## GOtta pull the specific links from the table I selected
```{r}
sfv_url <- read_html("https://www.eventhubs.com/tiers/sf5/")
tbls <- html_nodes(sfv_url, "table") 


all_characters <- tbls[1] %>%
      html_nodes("td a") %>%
      html_attr('href')


character_links <- paste0("https://www.eventhubs.com", all_characters)
## Remove extra /votes
character_links <- character_links[!str_detect(character_links, "/vote")]

table_out <- tbls %>% html_table()
teir_table <- table_out[[1]]

char_names <- teir_table$Character
```

The code below uses the SFV tier page to got through the data
```{r}
## Test section
char <- char_names[2]

#final_table <- NULL

## For loop goes through each characters webpage and scrapes their data

for (k in seq(char_names)) {
  char = char_names[k]
  
  #Get the html and pull out the tables
  html_hold <- character_links[k]
  webpage <- read_html(html_hold)
  
  tbls <- html_nodes(webpage, "table") 
  
  table_out <- tbls %>% html_table()
  ## Filter tables specifically to tables that include characters 
  filter_table <- table_out[lapply(table_out,
                                   function(x){colnames(x)[2]}) == "Character"]
  
  
  results_table <- do.call(rbind, filter_table)
  ## Generate the column that will be added into the final frame
  final_column <- results_table %>% select(Character, `Match avg.`) %>%
                    column_to_rownames(var = "Character")
  colnames(final_column) <- char
  ## If this is the first column we add an extra row including the current
  ## character as an NA. That column then becomes the first `final_table`
  if (char == char_names[1]) {
    missing_col <- NA
    final_column <- rbind(final_column, missing_col)
    rownames(final_column)[nrow(final_column)]  <- char
    final_table <- final_column
  }else{
    ## Else just bind the tables together after properly sorting on rownames
    ind <- match(rownames(final_table), rownames(final_column))
    sorted_col <- final_column[ind,,drop = F]
    final_table <- cbind(final_table,sorted_col)
  }
}
#final_table
## Order rows on columns (tier order)
ind <- match(colnames(final_table), rownames(final_table))

ordered_final_table <- final_table[ind,] 

## Print final tables
ordered_final_table


hist(as.matrix(ordered_final_table))

## I want to get a histogram of everything
hist_of_chars <- lapply(ordered_final_table, FUN = function(x){hist(x, main = names(x))})



```

Best Secondary for all Characters V0.1

```{r}
## Testing out stuff
ordered_final_table[,"Birdie", drop = FALSE]

k <- which(colnames(ordered_final_table) %in% "Birdie")

## The for loop below goes through each character and compares their matchup 
## spread to all other characters. If the secondary has better matchuos the  
## score will be higher. Otherwise the score will be low. This still results
## in a pseudo tier list, but a later function deals with it

for (k in seq(nrow(ordered_final_table) )) {
  ## Get char data and car columns
  char = colnames(ordered_final_table)[k]
  loop_table <- ordered_final_table[,-k]
  compare_col <-  ordered_final_table[,k,drop = FALSE]
  ## This apply isn't what we want it basically sorts on a pseudo tier list
  ## I need to find a way to properly do this with weighting peoples scores
     #secondary_out <- apply(loop_table, 2, function(x){sum(abs(compare_col - x),na.rm = T)})
  ## Idea, if birdie has a matchup that is 5.5 and Vega is 5.2 it should result in -0.3 to the score
  ## and if birdie has a matchup that is 4.8 and vega is 5 it should add .2
  
  ## This apply compares the loops character to all other characters, finding the
  ## difference between their matchup spread, if their matchups are more favorable
  ## they get a postive score, if less favorable they get a negative score
  ## This score is then added together to determine how well the other characters
  ## compliments the main character of the loop.
  secondary_out <- apply(loop_table, 2, function(x){sum(-(compare_col - x),na.rm = T)})
  ## Fixing names
  secondary_out <- c(NA, secondary_out)
  names(secondary_out)[1] <- char
  if (k == 1) {
    #Make table
    secondary_table <- as.data.frame(secondary_out)
    colnames(secondary_table)[k] <- char
  }else{
    #Sort table so it fits the laready made table
    ind <- match(rownames(secondary_table), names(secondary_out))
    sorted_sec <- secondary_out[ind]
    secondary_table <- cbind(secondary_table, sorted_sec)
    colnames(secondary_table)[k] <- char
  }
  
}

## The table of secondaries
secondary_table

## Testing data
(cbind(compare_col, ordered_final_table[,"Akuma"]))
sum(-(compare_col - ordered_final_table[,"Vega"]), na.rm = T)

## Function to get personal secondary table

secondary_ordered <- function(second_tabl, char){
  ### By using the previously generated table we can use this functiont to select
  ### a character and pull their best secondaries, and how the tier list changes
  ### compared to the optimal secondary list
  
  ## Pull main character, order on decreasing, remove main character
  temp_tab <- second_tabl[,char, drop = FALSE]
  temp_tab <- temp_tab[order(temp_tab,decreasing = T),, drop = FALSE]
  temp_tab <- temp_tab[!is.na(temp_tab),,drop = FALSE]
  ## Get tier list, but remove character again
  tier_filt <- rownames(second_tabl)[!(rownames(second_tabl) %in% char)]
  ## Combine numeric with teir list, and make sorted secondary list a column
  temp_tab <- cbind(temp_tab, tier_filt)
  temp_tab <- rownames_to_column(temp_tab, "Secondary Rank")
  colnames(temp_tab)[2:3] <- c("Secondary Score", "Current Tier List")
  ## Move around columns
  temp_tab <- select(temp_tab, `Secondary Score`, `Secondary Rank`, `Current Tier List`)
  ## Get the secondary rank change when compared to tier list
  `Tier Rank Change` <- match(temp_tab[,2], temp_tab[,3])- seq(nrow(temp_tab))
  ## Bind data together
  temp_tab <- cbind(temp_tab, `Tier Rank Change`) #%>%
    #mutate(`Tier Rank Change` = ifelse(`Current Tier List` == char, NA, `Tier Rank Change`))
  ## Return final output
  return(temp_tab)
  }

secondary_ordered(secondary_table, "Birdie")
secondary_ordered(secondary_table, "Sakura")
secondary_ordered(secondary_table, "Akuma")
secondary_ordered(secondary_table, "Vega")
```

Mega Loop

## GOtta pull the specific links from the table I selected
```{r}
tier_games_url <- read_html("https://www.eventhubs.com/tiers/")



tbls <- html_nodes(tier_games_url, "table") 

all_games <- tbls[3] %>%
      html_nodes("td a") %>%
      html_attr('href')

table_out <- tbls %>% html_table()
game_titles <- table_out[[3]][,2]

game_links <- paste0("https://www.eventhubs.com", all_games)
## Remove extra /
game_links <- unique(gsub("[/]$", "",game_links))
```

## GOtta pull the specific links from the table I selected
```{r}

game_chars_list <- list()
game_chars_name <- list()
for (k in seq(game_links)) {
  game_title <- game_titles[k]
  game_link <- game_links[k]


  game_url <- read_html(game_link)
  tbls <- html_nodes(game_url, "table") 
  
  
  all_characters <- tbls[1] %>%
        html_nodes("td a") %>%
        html_attr('href')
  
  
  character_links <- paste0("https://www.eventhubs.com", all_characters)
  ## Remove extra /votes
  character_links <- character_links[!str_detect(character_links, "/vote")]
  game_chars_list[[game_title]] <- character_links
  
  table_out <- tbls %>% html_table()
  teir_table <- table_out[[1]]
  
  game_chars_name[[game_title]] <- teir_table$Character
}
names(game_chars_list)
game_chars_list["Super Smash Bros. Melee"]
```


```{r}

all_character_matrix <- list()
skip_games <- c("Marvel vs. Capcom 2", "Skullgirls 2nd Encore",
                "Ultimate Marvel vs. Capcom 3",
                "Tatsunoko vs. Capcom", "Under Night In-Birth Exe:Late[st]")
for (j in seq(game_chars_list)) {
  game_name <- names(game_chars_list)[j]
  if (game_name %in% skip_games) {
    next
  }
    for (k in seq(game_chars_list[[j]])) {

  char_html = game_chars_list[[j]][k]
  char = game_chars_name[[j]][k]
  
  #Get the html and pull out the tables
  #html_hold <- character_links[k]
  webpage <- read_html(char_html)
  
  tbls <- html_nodes(webpage, "table") 
  
  table_out <- tbls %>% html_table()
  ## Filter tables specifically to tables that include characters 
  filter_table <- table_out[lapply(table_out,
                                   function(x){colnames(x)[2]}) == "Character"]
  
  
  results_table <- do.call(rbind, filter_table)
  #colnames(results_table) <- c("Character", "match avg.")
  ## Generate the column that will be added into the final frame
  final_column <- results_table %>% select(Character, `Match avg.`) %>%
                    column_to_rownames(var = "Character")
  colnames(final_column) <- char
  ## If this is the first column we add an extra row including the current
  ## character as an NA. That column then becomes the first `final_table`
  if (char == game_chars_name[[j]][1]) {
    missing_col <- NA
    final_column <- rbind(final_column, missing_col)
    rownames(final_column)[nrow(final_column)]  <- char
    final_table <- final_column
  }else{
    ## Else just bind the tables together after properly sorting on rownames
    ind <- match(rownames(final_table), rownames(final_column))
    sorted_col <- final_column[ind,,drop = F]
    final_table <- cbind(final_table,sorted_col)
  }
  

  }
  ind <- match(colnames(final_table), rownames(final_table))

  ordered_final_table <- final_table[ind,] 
  
  all_character_matrix[[game_name]] <- ordered_final_table
  
}

save(all_character_matrix, file = "all_tier_matrices.rda")
```


Secondary Maker
```{r}
load("all_games_n_chars.rda")
load("all_tier_matrices.rda")

second_matrix_games <- list()

for (j in seq(all_character_matrix)) {
  game_mat <- all_character_matrix[[j]]
  game_name <- names(all_character_matrix[j])
  
  for (k in seq(nrow(game_mat) )) {
    ## Get char data and car columns
    char = colnames(game_mat)[k]
    loop_table <- game_mat[,-k]
    compare_col <-  game_mat[,k,drop = FALSE]
    ## This apply isn't what we want it basically sorts on a pseudo tier list
    ## I need to find a way to properly do this with weighting peoples scores
       #secondary_out <- apply(loop_table, 2, function(x){sum(abs(compare_col - x),na.rm = T)})
    ## Idea, if birdie has a matchup that is 5.5 and Vega is 5.2 it should result in -0.3 to the score
    ## and if birdie has a matchup that is 4.8 and vega is 5 it should add .2
    
    ## This apply compares the loops character to all other characters, finding the
    ## difference between their matchup spread, if their matchups are more favorable
    ## they get a postive score, if less favorable they get a negative score
    ## This score is then added together to determine how well the other characters
    ## compliments the main character of the loop.
    secondary_out <- apply(loop_table, 2, function(x){sum(-(compare_col - x),na.rm = T)})
    ## Fixing names
    secondary_out <- c(NA, secondary_out)
    names(secondary_out)[1] <- char
    if (k == 1) {
      #Make table
      secondary_table <- as.data.frame(secondary_out)
      colnames(secondary_table)[k] <- char
    }else{
      #Sort table so it fits the laready made table
      ind <- match(rownames(secondary_table), names(secondary_out))
      sorted_sec <- secondary_out[ind]
      secondary_table <- cbind(secondary_table, sorted_sec)
      colnames(secondary_table)[k] <- char
    }
  }
  second_matrix_games[[game_name]] <- secondary_table 
}

head(second_matrix_games)


secondary_ordered(second_matrix_games$`Project M`, "Wario")

save(second_matrix_games, file = "secondary_matrix_all_games.rda")
```

