---
title: "Birdie Webscrape"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)

```
Get Birdie Webpage
```{r}
## Get webpage
webpage <- read_html("https://www.eventhubs.com/tiers/sf5/character/birdie/")

##Get tables of interest
tbls <- html_nodes(webpage, "table") 

table_out <- tbls %>% html_table()

filter_table <- table_out[1:3]
## Bind tables of interest
birdie_table <- do.call(rbind, filter_table)


birdie_table
```

## Notes/idea
- Maybe weight on the amount of votes each matchup gets
We can use each games page to scrape for chracter names

Prepare birdie table for being a part of the 
```{r}
birdie_table %>% select(Character, `Match avg.`) %>%
  column_to_rownames(var = "Character") %>%
  rename(Birdie = `Match avg.`)
```
Scrape the names of all the games
```{r}
tier_games_url <- read_html("https://www.eventhubs.com/tiers/")
tbls <- html_nodes(tier_games_url, "table") 

table_out <- tbls %>% html_table()
game_titles <- table_out[[3]][,2]
```
## GOtta pull the specific links from the table I selected
```{r}
tier_games_url <- read_html("https://www.eventhubs.com/tiers/")



tbls <- html_nodes(tier_games_url, "table") 

all_games <- tbls[3] %>%
      html_nodes("td a") %>%
      html_attr('href')

table_out <- tbls %>% html_table()
game_titles <- table_out[[3]][,2]

game_links <- paste0("https://www.eventhubs.com", all_games)
## Remove extra /
game_links <- unique(gsub("[/]$", "",game_links))
```

## GOtta pull the specific links from the table I selected
```{r}
sfv_url <- read_html("https://www.eventhubs.com/tiers/sf5/")
tbls <- html_nodes(sfv_url, "table") 


all_characters <- tbls[1] %>%
      html_nodes("td a") %>%
      html_attr('href')


character_links <- paste0("https://www.eventhubs.com", all_characters)
## Remove extra /votes
character_links <- character_links[!str_detect(character_links, "/vote")]

table_out <- tbls %>% html_table()
teir_table <- table_out[[1]]

char_names <- teir_table$Character
```

The code below uses the SFV tier page to got through the data
```{r}
## Test section
char <- char_names[2]

#final_table <- NULL

## For loop goes through each characters webpage and scrapes their data

for (k in seq(char_names)) {
  char = char_names[k]
  
  #Get the html and pull out the tables
  html_hold <- character_links[k]
  webpage <- read_html(html_hold)
  
  tbls <- html_nodes(webpage, "table") 
  
  table_out <- tbls %>% html_table()
  ## Filter tables specifically to tables that include characters 
  filter_table <- table_out[lapply(table_out,
                                   function(x){colnames(x)[2]}) == "Character"]
  
  
  results_table <- do.call(rbind, filter_table)
  ## Generate the column that will be added into the final frame
  final_column <- results_table %>% select(Character, `Match avg.`) %>%
                    column_to_rownames(var = "Character")
  colnames(final_column) <- char
  ## If this is the first column we add an extra row including the current
  ## character as an NA. That column then becomes the first `final_table`
  if (char == char_names[1]) {
    missing_col <- NA
    final_column <- rbind(final_column, missing_col)
    rownames(final_column)[nrow(final_column)]  <- char
    final_table <- final_column
  }else{
    ## Else just bind the tables together after properly sorting on rownames
    ind <- match(rownames(final_table), rownames(final_column))
    sorted_col <- final_column[ind,,drop = F]
    final_table <- cbind(final_table,sorted_col)
  }
}
#final_table
## Order rows on columns (tier order)
ind <- match(colnames(final_table), rownames(final_table))

ordered_final_table <- final_table[ind,] 

## Print final tables
ordered_final_table


hist(as.matrix(ordered_final_table))

## I want to get a histogram of everything
hist_of_chars <- lapply(ordered_final_table, FUN = function(x){hist(x, main = names(x))})



```

Best Secondary for all Characters V0.1

```{r}
## Testing out stuff
ordered_final_table[,"Birdie", drop = FALSE]

k <- which(colnames(ordered_final_table) %in% "Birdie")

## The for loop below goes through each character and compares their matchup 
## spread to all other characters. If the secondary has better matchuos the  
## score will be higher. Otherwise the score will be low. This still results
## in a pseudo tier list, but a later function deals with it

for (k in seq(nrow(ordered_final_table) )) {
  ## Get char data and car columns
  char = colnames(ordered_final_table)[k]
  loop_table <- ordered_final_table[,-k]
  compare_col <-  ordered_final_table[,k,drop = FALSE]
  ## This apply isn't what we want it basically sorts on a pseudo tier list
  ## I need to find a way to properly do this with weighting peoples scores
     #secondary_out <- apply(loop_table, 2, function(x){sum(abs(compare_col - x),na.rm = T)})
  ## Idea, if birdie has a matchup that is 5.5 and Vega is 5.2 it should result in -0.3 to the score
  ## and if birdie has a matchup that is 4.8 and vega is 5 it should add .2
  
  ## This apply compares the loops character to all other characters, finding the
  ## difference between their matchup spread, if their matchups are more favorable
  ## they get a postive score, if less favorable they get a negative score
  ## This score is then added together to determine how well the other characters
  ## compliments the main character of the loop.
  secondary_out <- apply(loop_table, 2, function(x){sum(-(compare_col - x),na.rm = T)})
  ## Fixing names
  secondary_out <- c(NA, secondary_out)
  names(secondary_out)[1] <- char
  if (k == 1) {
    #Make table
    secondary_table <- as.data.frame(secondary_out)
    colnames(secondary_table)[k] <- char
  }else{
    #Sort table so it fits the laready made table
    ind <- match(rownames(secondary_table), names(secondary_out))
    sorted_sec <- secondary_out[ind]
    secondary_table <- cbind(secondary_table, sorted_sec)
    colnames(secondary_table)[k] <- char
  }
  
}

## The table of secondaries
secondary_table

## Testing data
(cbind(compare_col, ordered_final_table[,"Akuma"]))
sum(-(compare_col - ordered_final_table[,"Vega"]), na.rm = T)

## Function to get personal secondary table

secondary_ordered <- function(second_tabl, char){
  ### By using the previously generated table we can use this functiont to select
  ### a character and pull their best secondaries, and how the tier list changes
  ### compared to the optimal secondary list
  
  ## Pull main character, order on decreasing, remove main character
  temp_tab <- second_tabl[,char, drop = FALSE]
  temp_tab <- temp_tab[order(temp_tab,decreasing = T),, drop = FALSE]
  temp_tab <- temp_tab[!is.na(temp_tab),,drop = FALSE]
  ## Get tier list, but remove character again
  tier_filt <- rownames(second_tabl)[!(rownames(second_tabl) %in% char)]
  ## Combine numeric with teir list, and make sorted secondary list a column
  temp_tab <- cbind(temp_tab, tier_filt)
  temp_tab <- rownames_to_column(temp_tab, "Secondary Rank")
  colnames(temp_tab)[2:3] <- c("Secondary Score", "Current Tier List")
  ## Move around columns
  temp_tab <- select(temp_tab, `Secondary Score`, `Secondary Rank`, `Current Tier List`)
  ## Get the secondary rank change when compared to tier list
  `Tier Rank Change` <- match(temp_tab[,2], temp_tab[,3])- seq(nrow(temp_tab))
  ## Bind data together
  temp_tab <- cbind(temp_tab, `Tier Rank Change`) #%>%
    #mutate(`Tier Rank Change` = ifelse(`Current Tier List` == char, NA, `Tier Rank Change`))
  ## Return final output
  return(temp_tab)
  }

secondary_ordered(secondary_table, "Birdie")
secondary_ordered(secondary_table, "Sakura")
secondary_ordered(secondary_table, "Akuma")
secondary_ordered(secondary_table, "Vega")
```

Mega Loop

## GOtta pull the specific links from the table I selected
```{r}
tier_games_url <- read_html("https://www.eventhubs.com/tiers/")



tbls <- html_nodes(tier_games_url, "table") 

all_games <- tbls[3] %>%
      html_nodes("td a") %>%
      html_attr('href')

table_out <- tbls %>% html_table()
game_titles <- table_out[[3]][,2]

game_links <- paste0("https://www.eventhubs.com", all_games)
## Remove extra /
game_links <- unique(gsub("[/]$", "",game_links))
```

## GOtta pull the specific links from the table I selected
```{r}

game_chars_list <- list()
game_chars_name <- list()
for (k in seq(game_links)) {
  game_title <- game_titles[k]
  game_link <- game_links[k]


  game_url <- read_html(game_link)
  tbls <- html_nodes(game_url, "table") 
  
  
  all_characters <- tbls[1] %>%
        html_nodes("td a") %>%
        html_attr('href')
  
  
  character_links <- paste0("https://www.eventhubs.com", all_characters)
  ## Remove extra /votes
  character_links <- character_links[!str_detect(character_links, "/vote")]
  game_chars_list[[game_title]] <- character_links
  
  table_out <- tbls %>% html_table()
  teir_table <- table_out[[1]]
  
  game_chars_name[[game_title]] <- teir_table$Character
}
names(game_chars_list)
game_chars_list["Super Smash Bros. Melee"]
```


```{r}

all_character_matrix <- list()
all_vote_matrix <- list()
skip_games <- c("Marvel vs. Capcom 2", "Skullgirls 2nd Encore",
                "Ultimate Marvel vs. Capcom 3",
                "Tatsunoko vs. Capcom", "Under Night In-Birth Exe:Late[st]")
for (j in seq(game_chars_list)) {
  game_name <- names(game_chars_list)[j]
  if (game_name %in% skip_games) {
    next
  }
    for (k in seq(game_chars_list[[j]])) {

  char_html = game_chars_list[[j]][k]
  char = game_chars_name[[j]][k]
  
  #Get the html and pull out the tables
  #html_hold <- character_links[k]
  webpage <- read_html(char_html)
  
  tbls <- html_nodes(webpage, "table") 
  
  table_out <- tbls %>% html_table()
  ## Filter tables specifically to tables that include characters 
  filter_table <- table_out[lapply(table_out,
                                   function(x){colnames(x)[2]}) == "Character"]
  
  
  results_table <- do.call(rbind, filter_table)
  #colnames(results_table) <- c("Character", "match avg.")
  ## Generate the column that will be added into the final frame
  final_column <- results_table %>% select(Character, `Match avg.`) %>%
                    column_to_rownames(var = "Character")
  colnames(final_column) <- char
  ##Add data frame for total votes
  final_vote_column <- results_table %>% select(Character, `Tot. votes`) %>%
                  column_to_rownames(var = "Character")
  colnames(final_vote_column) <- char
  ## If this is the first column we add an extra row including the current
  ## character as an NA. That column then becomes the first `final_table`
  if (char == game_chars_name[[j]][1]) {
    missing_col <- NA
    final_column <- rbind(final_column, missing_col)
    rownames(final_column)[nrow(final_column)]  <- char
    final_table <- final_column
    ## Final vote table
    missing_col <- NA
    final_vote_column <- rbind(final_vote_column, missing_col)
    rownames(final_vote_column)[nrow(final_vote_column)]  <- char
    final_vote_table <- final_vote_column
  }else{
    ## Else just bind the tables together after properly sorting on rownames
    ind <- match(rownames(final_table), rownames(final_column))
    sorted_col <- final_column[ind,,drop = F]
    final_table <- cbind(final_table,sorted_col)
    ## Final vote version
    sorted_col <- final_vote_column[ind,,drop = F]
    final_vote_table <- cbind(final_vote_table,sorted_col)
  }
  

  }
  ind <- match(colnames(final_table), rownames(final_table))

  ordered_final_table <- final_table[ind,] 
  ordered_final_votes <- final_vote_table[ind,]
  all_character_matrix[[game_name]] <- ordered_final_table
  all_vote_matrix[[game_name]] <- ordered_final_votes
  
}

lapply(all_vote_matrix, function(x){
  colnames(x) <- rownames(x)
})

save(all_character_matrix, all_vote_matrix, file = "all_tier_matrices.rda")
```


Secondary Maker
```{r}
load("all_games_n_chars.rda")
load("all_tier_matrices.rda")

second_matrix_games <- list()

for (j in seq(all_character_matrix)) {
  game_mat <- all_character_matrix[[j]]
  game_name <- names(all_character_matrix[j])
  
  for (k in seq(nrow(game_mat) )) {
    ## Get char data and car columns
    char = colnames(game_mat)[k]
    loop_table <- game_mat[,-k]
    compare_col <-  game_mat[,k,drop = FALSE]
    ## This apply isn't what we want it basically sorts on a pseudo tier list
    ## I need to find a way to properly do this with weighting peoples scores
       #secondary_out <- apply(loop_table, 2, function(x){sum(abs(compare_col - x),na.rm = T)})
    ## Idea, if birdie has a matchup that is 5.5 and Vega is 5.2 it should result in -0.3 to the score
    ## and if birdie has a matchup that is 4.8 and vega is 5 it should add .2
    
    ## This apply compares the loops character to all other characters, finding the
    ## difference between their matchup spread, if their matchups are more favorable
    ## they get a postive score, if less favorable they get a negative score
    ## This score is then added together to determine how well the other characters
    ## compliments the main character of the loop.
    secondary_out <- apply(loop_table, 2, function(x){sum(-(compare_col - x),na.rm = T)})
    ## Fixing names
    secondary_out <- c(NA, secondary_out)
    names(secondary_out)[1] <- char
    if (k == 1) {
      #Make table
      secondary_table <- as.data.frame(secondary_out)
      colnames(secondary_table)[k] <- char
    }else{
      #Sort table so it fits the laready made table
      ind <- match(rownames(secondary_table), names(secondary_out))
      sorted_sec <- secondary_out[ind]
      secondary_table <- cbind(secondary_table, sorted_sec)
      colnames(secondary_table)[k] <- char
    }
  }
  second_matrix_games[[game_name]] <- secondary_table 
}

head(second_matrix_games)


secondary_ordered(second_matrix_games$`Guilty Gear Xrd REV 2`, "Potemkin")

#save(second_matrix_games, file = "secondary_matrix_all_games.rda")
```
## Secondary Maker Winners Only aka Jon's Idea
Jon has the idea that instead of taking all matchups into account for the secondary matrix we should only be looking at matchups where a character outperforms the main. So this cares less about overall matchup spread between the two characters, but focuses on the matchup spread based on ones main.

```{r}
second_matrix_games_jon <- list()

for (j in seq(all_character_matrix)) {
  game_mat <- all_character_matrix[[j]]
  game_name <- names(all_character_matrix[j])
  
  for (k in seq(nrow(game_mat) )) {
    ## Get char data and car columns
    char = colnames(game_mat)[k]
    loop_table <- game_mat[,-k]
    compare_col <-  game_mat[,k,drop = FALSE]
    ## This apply isn't what we want it basically sorts on a pseudo tier list
    ## I need to find a way to properly do this with weighting peoples scores
       #secondary_out <- apply(loop_table, 2, function(x){sum(abs(compare_col - x),na.rm = T)})
    ## Idea, if birdie has a matchup that is 5.5 and Vega is 5.2 it should result in -0.3 to the score
    ## and if birdie has a matchup that is 4.8 and vega is 5 it should add .2
    
    ## This apply compares the loops character to all other characters, finding the
    ## difference between their matchup spread, if their matchups are more favorable
    ## they get a positive score, if less favorable they get a negative score
    ## This score is then added together to determine how well the other characters
    ## compliments the main character of the loop.
    secondary_out <- apply(loop_table, 2, function(x){
      init_compare <- -(compare_col - x)
      jon_compare <- init_compare[init_compare > 0]
      sum(jon_compare, na.rm = TRUE)
      })
    
    ## Fixing names
    secondary_out <- c(NA, secondary_out)
    names(secondary_out)[1] <- char
    if (k == 1) {
      #Make table
      secondary_table <- as.data.frame(secondary_out)
      colnames(secondary_table)[k] <- char
    }else{
      #Sort table so it fits the laready made table
      ind <- match(rownames(secondary_table), names(secondary_out))
      sorted_sec <- secondary_out[ind]
      secondary_table <- cbind(secondary_table, sorted_sec)
      colnames(secondary_table)[k] <- char
    }
  }
  second_matrix_games_jon[[game_name]] <- secondary_table 
}

head(second_matrix_games_jon)


secondary_ordered(second_matrix_games_jon$`Guilty Gear Xrd REV 2`, "Potemkin")

save(second_matrix_games, second_matrix_games_jon, file = "secondary_matrix_all_games.rda")
save(second_matrix_games, second_matrix_games_jon, file = "secondary_selector/secondary_matrix_all_games.rda")
```


Character comparison function

```{r}
load("secondary_matrix_all_games.rda")


game_matrix <- all_character_matrix$`Guilty Gear Xrd REV 2`
character_1 <- "Potemkin"
character_2 <- "Slayer"
secondary_comparison <- function(game_matrix, character_1, character_2){
  temp_dat <- as.data.frame(game_matrix[,c(character_1, character_2)])
  temp_dat <- temp_dat[!(rownames(temp_dat) %in% c(character_1, character_2)),]
  temp_dat <- cbind(temp_dat, temp_dat[[2]] - temp_dat[[1]])
  colnames(temp_dat)[3] <- "secondary gains"
  
  return(temp_dat)
}


secondary_comparison(all_character_matrix$`Street Fighter 5: Champion Edition`,
                     "Sakura",
                     "Sagat")

secondary_comparison(all_character_matrix$`Street Fighter 5: Champion Edition`,
                     "Sakura",
                     "Abigail")


secondary_comparison(all_character_matrix$`Guilty Gear Xrd REV 2`,
                     "Potemkin",
                     "Slayer")
```

```{r}
off_capcom_url <- "https://game.capcom.com/cfn/sfv/stats/dia/202011"

character_order <- c("E. Honda",
                      "Urien",
                      "M. Bison",
                      "Balrog",
                      "Vega",
                      "Ed",
                      "Blanka",
                      "Abigail",
                      "Dhalsim",
                      "Alex",
                      "Birdie",
                      "Falke",
                      "Guile",
                      "Cody",
                      "F.A.N.G",
                      "Zangief",
                      "Laura",
                      "G",
                      "Poison",
                      "Sagat",
                      "Ibuki",
                      "Karin",
                      "Kolin",
                      "Zeku",
                      "Necalli",
                      "Lucia",
                      "Gill",
                      "Juri",
                      "Nash",
                      "Chun-Li",
                      "Ryu",
                      "Ken",
                      "Seth",
                      "Kage",
                      "R. Mika",
                      "Sakura",
                      "Akuma",
                      "Menat",
                      "Cammy",
                      "Rashid"
                    )
sfv_chars <- rownames(second_matrix_games$`Street Fighter 5: Champion Edition`)

sfv_chars[!(sfv_chars %in%  character_order)]


sfv_url <- read_html(off_capcom_url)
tbls <- html_nodes(sfv_url, "table") 


table_out <- tbls %>% html_table()
official_table  <- table_out[[1]]
colnames(official_table) <- c("average", character_order)
rownames(official_table) <- character_order

## Get averages
official_averages <- official_table[,1,drop = F]

matchup_df <- official_table[,-1]
matchup_df[matchup_df == "-"] <- NA

matchup_matrix <- t((matchup_df))
matchup_matrix <- mapply(matchup_matrix, FUN=as.numeric)
matchup_matrix <- matrix(data=matchup_matrix, ncol=ncol(matchup_df),
                         nrow=nrow(matchup_df))
rownames(matchup_matrix) <- rownames(matchup_df) ;colnames(matchup_matrix) <- colnames(matchup_df)

## Pull image links so I don't always have to update this by hand/
all_images <-  tbls %>%
        html_nodes("img") %>%
        html_attr('src')

uni_images <- unique(all_images)

character_library <- cbind(character_order, uni_images)
colnames(character_library) <- c("character", "capcom_images")
write.csv(character_library, "sfv_character_image_library.csv", row.names = F)

hist(matchup_matrix)

### SO BEAUTIFUL (but its built to be like that soooo)
hist(as.numeric(official_averages$average))
## Uh not very balanced.




```
Official secondary matrix, this isn't working, figure it out tomorrow.
```{r}
for (k in seq(nrow(matchup_matrix) )) {
  ## Get char data and car columns
  char = colnames(matchup_matrix)[k]
  loop_table <- matchup_matrix[,-k]
  compare_col <-  matchup_matrix[,k,drop = FALSE]
  ## This apply isn't what we want it basically sorts on a pseudo tier list
  ## I need to find a way to properly do this with weighting peoples scores
     #secondary_out <- apply(loop_table, 2, function(x){sum(abs(compare_col - x),na.rm = T)})
  ## Idea, if birdie has a matchup that is 5.5 and Vega is 5.2 it should result in -0.3 to the score
  ## and if birdie has a matchup that is 4.8 and vega is 5 it should add .2
  
  ## This apply compares the loops character to all other characters, finding the
  ## difference between their matchup spread, if their matchups are more favorable
  ## they get a postive score, if less favorable they get a negative score
  ## This score is then added together to determine how well the other characters
  ## compliments the main character of the loop.
  secondary_out <- apply(loop_table, 2, function(x){sum(-(compare_col - x),na.rm = T)})
  ## Fixing names
  secondary_out <- c(NA, secondary_out)
  names(secondary_out)[1] <- char
  if (k == 1) {
    #Make table
    secondary_table <- as.data.frame(secondary_out)
    colnames(secondary_table)[k] <- char
  }else{
    #Sort table so it fits the laready made table
    ind <- match(rownames(secondary_table), names(secondary_out))
    sorted_sec <- secondary_out[ind]
    secondary_table <- cbind(secondary_table, sorted_sec)
    colnames(secondary_table)[k] <- char
  }
  
}

## The table of secondaries
secondary_table

sec_comp <- secondary_comparison(matchup_matrix, "E. Honda", "Ed")
sec_comp
sum(sec_comp$`secondary gains`)

secondary_ordered(secondary_table, "Birdie")
```

```{r}
secondary_ordered(second_matrix_games$`Super Smash Bros. Melee`,
                  char = "Peach")
```

